Supplmentary material - A plot is worth a thousand tests: assessing residual diagnostics with visual inference

### 2023-03-28 paper_comparison/appendix.Rmd
don't need the x_dist part in appendix

lower_p <- map_df(c(0.125, 0.25, 0.5), function(modified) {
  calc_p_value_multi(vi_survey %>%
                       filter(!attention_check) %>%
                       filter(!null_lineup) %>%
                       filter(x_dist == "uniform") %>%
                       mutate(alpha_lower = alpha * (1 - modified)),
                     lineup_id = unique_lineup_id,
                     detect = detect,
                     n_sel = num_selection,
                     alpha = alpha_lower) %>%
  mutate(modified = modified) %>%
  mutate(adjusted_p_value = p_value)
})

@@

## Curious effect of predictor distribution on conventional test power

```{r cache = TRUE}
min_poly_es <- vi_survey %>% 
  filter(!null_lineup, 
         !attention_check,
         type == "polynomial", 
         x_dist == "uniform") %>%
  pull(effect_size) %>%
  min()

max_poly_es <- vi_survey %>% 
  filter(!null_lineup, 
         !attention_check,
         type == "polynomial", 
         x_dist == "uniform") %>%
  pull(effect_size) %>%
  max()

min_heter_es <- vi_survey %>% 
  filter(!null_lineup, 
         !attention_check,
         type == "heteroskedasticity", 
         x_dist == "uniform") %>%
  pull(effect_size) %>%
  min()

max_heter_es <- vi_survey %>% 
  filter(!null_lineup, 
         !attention_check,
         type == "heteroskedasticity", 
         x_dist == "uniform") %>%
  pull(effect_size) %>%
  max()

poly_x_dist <- poly_conv_sim %>%
  select(-RESET3_p_value, -(RESET5_p_value:RESET10_p_value), -F_p_value) %>%
  rename(RESET_p_value = RESET4_p_value) %>%
  pivot_longer(RESET_p_value:SW_p_value) %>%
  mutate(name = gsub("_p_value", " test", name)) %>%
  filter(name == "RESET test") %>%
  mutate(reject = value <= 0.05) %>%
  select(effect_size, name, x_dist, reject) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(type = "non-linearity")

heter_x_dist <- heter_conv_sim %>%
  select(-RESET3_p_value, -(RESET5_p_value:RESET10_p_value), -F_p_value) %>%
  rename(RESET_p_value = RESET4_p_value) %>%
  pivot_longer(RESET_p_value:SW_p_value) %>%
  mutate(name = gsub("_p_value", " test", name)) %>%
  filter(name == "BP test") %>%
  mutate(reject = value <= 0.05) %>%
  select(effect_size, name, x_dist, reject) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_heter_es, max_heter_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(type = "heteroskedasticity")
```

```{r conv-x-dist, fig.cap = "Change of power of conventional tests under different fitted value distribution for non-linearity model and heteroskedasticity model.", fig.height = 3}
bind_rows(poly_x_dist, heter_x_dist) %>%
  mutate(type = factor(type, levels = c("non-linearity", "heteroskedasticity"))) %>%
  ggplot() +

  # Draw conventional test power curve
  geom_line(aes(log_effect_size, power, col = x_dist),
            size = 1) +

  # Theme
  theme_light() +
  scale_color_manual(values = rev(rcartocolor::carto_pal(4, "Vivid"))) +
  xlab(expression(log[e] (Effect_size))) +
  ylab("Power") +
  labs(col = "", size = "# lineups") +
  facet_wrap(~type, scales = "free_x")
```

@@

```{r cache = TRUE}
reset_diff_dat <- poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  select(-F_p_value, -BP_p_value, -SW_p_value) %>%
  pivot_longer(RESET3_p_value:RESET10_p_value) %>%
  mutate(name = gsub("RESET(.*)_p_value", "\\1", name)) %>%
  mutate(reject = value <= 0.05) %>%
  select(effect_size, name, reject) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size))
```

>>>>

lower_p <- map_df(c(0.125, 0.25, 0.5), function(modified) {
  calc_p_value_multi(vi_survey %>%
                       filter(!attention_check) %>%
                       filter(!null_lineup) %>%
                       filter(x_dist == "uniform") %>%
                       mutate(alpha_lower = alpha * (1 - modified)),
                     lineup_id = unique_lineup_id,
                     detect = detect,
                     n_sel = num_selection,
                     alpha = alpha_lower) %>%
  mutate(modified = 1 - modified) %>%
  mutate(adjusted_p_value = p_value)
})

@@

@@

```{r cache = TRUE}
reset_diff_dat <- poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  filter(shape == 4) %>%
  select(-F_p_value, -BP_p_value, -SW_p_value) %>%
  pivot_longer(RESET3_p_value:RESET10_p_value) %>%
  mutate(name = gsub("RESET(.*)_p_value", "\\1", name)) %>%
  mutate(reject = value <= 0.05) %>%
  select(effect_size, name, reject) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size))
```

```{r cache = TRUE}
reset_diff_dat <- poly_conv_sim %>%
  filter(x_dist == "uniform") %>%
  filter(shape == 1) %>%
  select(-F_p_value, -BP_p_value, -SW_p_value) %>%
  pivot_longer(RESET3_p_value:RESET10_p_value) %>%
  mutate(name = gsub("RESET(.*)_p_value", "\\1", name)) %>%
  mutate(reject = value <= 0.05) %>%
  select(effect_size, name, reject) %>%
  mutate(offset0 = log(0.05/0.95)) %>%
  nest(dat = c(effect_size, offset0, reject)) %>%
  mutate(mod = map(dat, 
                   ~glm(reject ~ effect_size - 1, 
                        family = binomial(), 
                        data = .x,
                        offset = offset0))) %>%
  mutate(power = map(mod, function(mod) {
    result <- data.frame(effect_size = seq(min_poly_es, max_poly_es, 0.1),
                         offset0 = log(0.05/0.95))
    result$power <- predict(mod, type = "response", newdata = result)
    result
  })) %>%
  select(-dat, -mod) %>%
  unnest(power) %>%
  mutate(log_effect_size = log(effect_size))
```
